Building Sustainable Software - The CSDMS Approach

### 2015-03-02 article.tex
Renamed tex and bib files as "article".
Removed abstract and authors for JORS submission.

\usepackage[bookmarks, bookmarksopen, bookmarksnumbered]{hyperref}
\usepackage[all]{hypcap}
\urlstyle{rm}

@@

\author{
  Eric W. H. Hutton$^{\dag}$,
  Mark D. Piper$^{\dag}$,
  Scott D. Peckham$^{\dag}$,
  Irina Overeem$^{\dag}$,
  Albert J. Kettner$^{\dag}$,
  James P. M. Syvitski$^{\dag}$,
}

@@

\begin{abstract}

\csdms{}, The Community Surface Dynamics Modeling System, is an NSF funded
project whose focus is to aid a diverse community of earth and ocean system
model \emph{users} and \emph{developers} to use and create robust software
quickly.  To this end, \csdms{} develops, integrates, archives and disseminates
earth-system models and tools to an international (67 country) community
with the goal of building the set of tools necessary to model
earth surface processes. Modelers use \csdms{} for access to over two hundred open
source surface-dynamics models and tools, as well as model metadata. Such a
model repository increases model transparency and helps eliminate
duplication by presenting the current state of community modeling efforts.
To increase software sustainability, composability and interoperability,
\csdms{} promotes standards that define common modeling interfaces, semantic
mediation between models, and model metadata. Through online resources and
workshops, \csdms{} promotes software engineering best practices, which are
less familiar to many within our community. For example,
version control, unit testing, continuous integration, test-driven
development, and well-written \emph{clean code} are all topics of the
educational mission of \csdms{}.

\end{abstract}

@@

The \csdms{} \emph{Standard Names}
\footnote{https://github.com/csdms/standard\_names}
are a common language for variable names exchanged between models. They play
an important role in the \bmi{} as they provide a mapping of a model's
internal variable names to a common language used by the \bmi{} getter and
setter functions.

@@

\bibliographystyle{plain}

\bibliography{wssspe-citations}{}

>>>>

\usepackage[bookmarks, bookmarksopen, bookmarksnumbered]{hyperref}
\usepackage[all]{hypcap}
\usepackage{doi}
\urlstyle{rm}

@@

%\author{
%  Eric W. H. Hutton$^{\dag}$,
%  Mark D. Piper$^{\dag}$,
%  Scott D. Peckham$^{\dag}$,
%  Irina Overeem$^{\dag}$,
%  Albert J. Kettner$^{\dag}$,
%  James P. M. Syvitski$^{\dag}$,
%}

@@

%\begin{abstract}

%\csdms{}, The Community Surface Dynamics Modeling System, is an NSF funded
%project whose focus is to aid a diverse community of earth and ocean system
%model \emph{users} and \emph{developers} to use and create robust software
%quickly.  To this end, \csdms{} develops, integrates, archives and disseminates
%earth-system models and tools to an international (67 country) community
%with the goal of building the set of tools necessary to model
%earth surface processes. Modelers use \csdms{} for access to over two hundred open
%source surface-dynamics models and tools, as well as model metadata. Such a
%model repository increases model transparency and helps eliminate
%duplication by presenting the current state of community modeling efforts.
%To increase software sustainability, composability and interoperability,
%\csdms{} promotes standards that define common modeling interfaces, semantic
%mediation between models, and model metadata. Through online resources and
%workshops, \csdms{} promotes software engineering best practices, which are
%less familiar to many within our community. For example,
%version control, unit testing, continuous integration, test-driven
%development, and well-written \emph{clean code} are all topics of the
%educational mission of \csdms{}.

%\end{abstract}

@@

The \csdms{} \emph{Standard Names}
\footnote{https://github.com/csdms/standard\_names}
are a common language for variable names exchanged between models
~\cite{peckham2014csdms}. They play
an important role in the \bmi{} as they provide a mapping of a model's
internal variable names to a common language used by the \bmi{} getter and
setter functions.

@@

\bibliographystyle{plainurl}

\bibliography{article-citations}{}
